---
title: "Introduction to PMXploit"
author: "Patrick Nolain"
date: "`r Sys.Date()`"
output:
  html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to pmxploit}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 4.5
)
```

The present article describes briefly how to use `pmxploit` from `R`.

```{r, message=FALSE}
library(pmxploit)
library(knitr)
library(tidyverse)

theme_set(theme_pmx())
```


# Load a NONMEM run archive

```{r, eval=FALSE}
run <- load_nm_run(path = "path/to/my_run_archive.tar.gz")
```

```{r, echo=FALSE}
run <- pmxploit:::EXAMPLERUN
```

# Job details

## Run information

### Model/Data/Files

```{r, warning=FALSE}
run$info %>% 
  bind_cols() %>% 
  select(run_name, dataset_file, control_stream_file, nodes, nm_version, number_of_subjects, number_of_observations, duration) %>% 
  mutate(duration = as.character(lubridate::as.period(duration))) %>% 
  gather(property, value) %>% 
  kable()
```

### Estimation

```{r}
# Estimation steps summary
run$estimations %>%
  map(~ .[c("title", "final_ofv", "minimization", "duration")]) %>% 
  bind_rows(.id= "n_estimation") %>% 
  kable()
```

## Model information

### Compartments

```{r}
kable(run$model$compartments)
```

### Parameters

```{r}
run$model$parameters %>% 
  filter(type %in% c("theta", "eta")) %>% 
  select(id, type, name) %>% 
  kable()
```

### Covariates

```{r}
kable(run$model$covariates)
```

# Diagnostic plots

## Spaghetti plot

```{r, fig.height=5}
run %>% 
  group_by(SEX) %>% 
  plot_observed_profiles(compartment = 2, y_scale = "log", facetted = FALSE)
```

## Dependent variable observations vs predictions

```{r}
plot_dv_vs_predictions(run, compartment = 2, predictions = c("PRED", "IPRED"))
plot_dv_vs_predictions(run, compartment = 2, predictions = c("PRED", "IPRED"), x_scale = "log", y_scale = "log")
```

## Residuals

```{r}
plot_residuals(run, compartment = 2, residuals = "CWRES", regressor = c("PRED", "TIME"), reference_value = 2)

plot_residuals(run, compartment = 2, residuals = c("CWRES"), type = "histogram")
```

## Individual predictions profiles

```{r}
plot_individual_profiles(run, compartment = 2, ids = 1:4, predictions = c("PRED", "IPRED"), y_scale = "log")
```

# Population parameters

## THETA

```{r}
last_estimation <- last(run$estimations)

last_estimation$thetas %>% 
  mutate(rse = scales::percent(rse)) %>% 
  kable()
```

### Convergence

```{r}
plot_convergence(run, parameters = "theta")
```

## OMEGA

```{r}
# OMEGA matrix
kable(last_estimation$omega_matrix)

# OMEGA matrix as a table, with RSE% and IC 95%
last_estimation$omega %>% 
  mutate(rse = scales::percent(rse)) %>% 
  kable()
```

## Shrinkage

```{r}1
last_estimation$shrinkage %>% 
  mutate(shrinkage = scales::percent(shrinkage)) %>% 
  kable()
```

# Individuals

## Parameters

### Distributions

```{r}
summarize_parameters_distributions(run)

plot_parameters_distributions(run, parameters = "eta")

run %>% 
  group_by(STUD) %>%
  plot_parameters_distributions(parameters = c("CL", "V1"), type = "boxplot")
```

### Correlations

```{r}
summarize_parameters_correlations(run, parameters = "individual")

plot_parameters_correlations(run, parameters = "eta", type = "heatmap")
```

## Continuous covariates

### Distributions

```{r}
summarize_continuous_covariates(run)

plot_continuous_covariates_distributions(run)
run %>% 
  group_by(STUD) %>%
  plot_continuous_covariates_distributions(type = "boxplot")
```

### Correlations

```{r}
summarize_covariates_correlations(run)

plot_covariates_correlations(run, type = "heatmap")

run %>% 
  group_by(STUD) %>%
  plot_covariates_correlations(type = "scatterplot")
```

## Parameters vs covariates

```{r, message=FALSE, warning=FALSE}
plot_parameters_vs_continuous_covariates(run)

plot_parameters_vs_categorical_covariates(run, parameters = c("CL", "V1"))
```

# Quality criteria

```{r}
# Overall QC
qc <- quality_criteria(run, predictions = "PRED")

# QC by study
qc_stud <- run %>% 
  group_by(STUD) %>%
  quality_criteria(predictions = "PRED")

kable(qc$standard)

qc_stud %>% 
  select(Study, standard) %>% 
  unnest() %>% 
  kable()

# Bias
qc_stud %>% 
  select(Study, bias) %>% 
  unnest() %>% 
  mutate(relative_value = scales::percent(relative_value)) %>% 
  rename(`Mean Prediction Error (%)` = relative_value) %>% 
  kable()

# Precision
qc_stud %>% 
  select(Study, precision) %>% 
  unnest() %>% 
  mutate(relative_value = scales::percent(relative_value)) %>% 
  rename(`Root Mean Square Error (%)` = relative_value) %>% 
  kable()
```


